\section*{Dedication}

\textit{To my beloved Yeganeh}

\newpage

\section*{Acknowledgements}

First, I would like to thank my advisor, Pedro Cardoso-Leite, for his generosity and kindness, and for creating an environment where I felt safe, valued, and supported to pursue my research interests. Thank you for your tireless skepticism and tough questioning that have improved me in countless ways. I am very grateful for your patience and kindness, and very fortunate to have had the opportunity to work with you.

I would like to thank my co-advisor, Jöran Lepsein, and committee members, Florian Waszak, and Christine Schiltz for the comments, discussions, and encouragement in the annual meetings. Paul Schrater in particular has been always helpful in the early stages of my research, and again in the final stages of it. I want to thank him for his scientific wisdom and thoughtful guidance. I would also like to thank Daphne Bavelier and Julia Föcker for the opportunity to learn from them and their generosity in providing valuable data for my research. I am very fortunate to have been inspired by your work and to have received your feedback on my own.

To have been granted the opportunity to pursue PhD studies has indeed been an immense privilege. For that, I would like to thank University of Luxembourg and Max Planck Institute for Human Cognitive and Brain Sciences. I am also grateful for the financial support from Luxembourg National Research Fund. The studies in this thesis were supported by the Luxembourg National Research Fund through the project DIGILEARN. Luxembourg is a wonderful place to live and work, and I am very grateful for the opportunity to have been able to live and work here.

I would also like to thank my friends and family for their love and support, and for being by my side the whole way. I want to extend a special thanks to Saeed Gholami Shahbandi and Shayan Eslami for their genuine and unwavering friendship. Thank you to my parents, my sister, and my bother for their support in everything I have pursued. Thanks also to my friends for contributing to an enjoyable life outside of research, especially Sherwin Ahmadi Fouladi, Mani Monajjemi, Safa Jamali, Soheil Asmari, and Hamid Gholami Shahbandi (and not to forget Marmeladov, Taguchi, and Twigi). And for our many impromptu conversations about cognition and computing, I thank Ali Farjami and Mostafa Salari Rad. As well, I would like to thank members of the xCIT Lab for all the discussions and contributions: Dominic Mussack, Brice Clocher, Aurélien Defossez, Emmanuel Schmück, and Kamelia Jamaati.

Then, I want to thank my partner in science and life (and now wife), Yeganeh Farhzadi, for always believing in me and providing me with love and support, for building and protecting an environment where even silly and awkward ideas are treasured, and for being my best friend. Since 2015, we went through the ups and downs of life together, and I look forward to the rest of it. Thank you Yeganeh, very much. I love you.

As a final note, I would like to thank all the people who have inspired me through their work and lives. For that, it would be remiss of me not to acknowledge all the Iranian people; my many thanks go out to "woman, life, freedom".


